Security of deployed Android devices

### 2013-10-22 securityupdates.tex
99.9% of devices have good version strings for OS versions so we don't need to worry about that

\subsection{Versions of Android running on devices}
We also need historical information on which versions of Android were running on devices along with other information about those devices which allows us to go into more detail and confirm the reliability of the data our results depend on.
The only suitable data which is available for this is the DeviceAnalyzer data~\cite{TODO}.
The DeviceAnalyzer data contains data from ??? devices with a total of ??? device days, it contains data for more than ??? months for ??? devices.
%TODO talk about the DeviceAnalyzer project a bit
Various different kinds of data\footnote{\url{TODO}} are collected by the DeviceAnalyzer Android app\footnote{\url{TODO}}.
Among these are the build string and API version for the version of Android currently running on the device each day.
The API/SDK version is a well defined integer, however it does not always change with new Android releases, particularly security bug fixes should not increase this value.
The build string is `The user-visible version string', fortunately most devices in the data have a build string of the form `x.y.z random string' and so it is possible to extract the Android version number.
%TODO count proportion of device days where the build string cannot be interpreted

>>>>

\subsection{Versions of Android running on devices}
We also need historical information on which versions of Android were running on devices along with other information about those devices which allows us to go into more detail and confirm the reliability of the data our results depend on.
The only suitable data which is available for this is the DeviceAnalyzer data~\cite{TODO}.
The DeviceAnalyzer data contains data from ??? devices with a total of ??? device days, it contains data for more than ??? months for ??? devices.
%TODO talk about the DeviceAnalyzer project a bit
Various different kinds of data\footnote{\url{TODO}} are collected by the DeviceAnalyzer Android app\footnote{\url{TODO}}.
Among these are the build string and API version for the version of Android currently running on the device each day.
The API/SDK version is a well defined integer, however it does not always change with new Android releases, particularly security bug fixes should not increase this value.
The build string is `The user-visible version string', fortunately most (99.9\%) devices in the data have a build string of the form `x.y.z random string' and so it is possible to extract the Android version number.
